---
title: "R Notebook"
output: html_notebook
---

Explanation: This code uses the superComputer's output and transforms it to a general dataBase *DF_total_complete.csv* and *DF_finalTime_complete.csv*. It is not necessary to run it if one starts from those csv. It only works if we have downloaded the output of the superComputer in the **DF_total** and **DF_finalTime** directories.

1. Procedure to reduce the number of steps for visualization. Run only once. 


2. Merge all data frames to a big data frame for visualizations


```{r}
#enter the file with all the new reduced data frames and merge them 

setwd("../../dataPatung_descargado/salida/DF_spatialAverage/")
library(plyr)
DF_spatial <- ldply(list.files(), read.csv, header=TRUE)
# it is important to detach plyr for dplyr to be used
detach(package:plyr)
```
```{r}
write.csv(DF_spatial, "../../data/DF_spatialAverage_complete.csv", row.names = FALSE)
```


```{r}
#enter the file with all the new reduced data frames and merge them 

setwd("../../dataPatung_descargado/salida/DF_muestrasPath/")
library(plyr)
DF_sample <- ldply(list.files(), read.csv, header=TRUE)
# it is important to detach plyr for dplyr to be used
detach(package:plyr)
```
```{r}
write.csv(DF_sample, "../../data/DF_muestrasPath_complete.csv", row.names = FALSE)
```

```{r}
#enter the file with all the new reduced data frames and merge them 

setwd("../../dataPatung_descargado/salida/DF_total/")
library(plyr)
DF_total <- ldply(list.files(), read.csv, header=TRUE)
# it is important to detach plyr for dplyr to be used
detach(package:plyr)
```
```{r}
write.csv(DF_total, "../../data/DF_total_TF.csv", row.names = FALSE)
```





```{r}
#enter the file with all the new reduced data frames and merge them 

#setwd("./DF_total/")
#library(plyr)
#DF_total_complete <- ldply(list.files(), read.csv, header=TRUE)
# it is important to detach plyr for dplyr to be used
#detach(package:plyr)
```
```{r}
#write.csv(DF_total_complete, "../../data/DF_total_complete.csv", row.names = FALSE)
```




