---
title: "R Notebook"
output: html_notebook
---

We first run the libraries and colors

```{r}
library(ggplot2)
library(viridis)
library(dplyr)
library(tidyverse)
library(reshape2)
library(TAM)

#base de datos general de colores:
mycols <- c("#021128","#1b4a64", "#3585a0", "#759580", "#c78f34", "#fd9706","#fdb81c","#fbdb30")
mycols2 <- c("#1b4a64", "#fd9706")
mycols3 <- c("#1b4a64", "#fd9706", "black")
mycols3_white <- c("#1b4a64", "#fd9706", "#eeeeee")

colorsDis <- c("#B87400","white")
colorsDis2 <- c("#B87400","#555555")
colorsDis3 <- c("#111111","#8B0000","#fd9706")

```

We download the data of the movement of the workers during harvesting

```{r}
#DF_SAM<- read.csv("./archivosTrabajandose/toyModelHarvest/data/DF_muestrasPath_complete.csv")
DF_SAM <- read.csv("../../data/DF_muestrasPath_complete.csv", header = TRUE)

#As we defined the model for SI and SF (not used at the end), SI only infects in the first half of the time
# and then it harvest, but do not infect anymore. 

DF_SAM_SI <- DF_SAM %>% filter(porcionCosecha == "S_I")
DF_SAM_SF <- DF_SAM %>% filter(porcionCosecha == "S_F")
DF_SAM_A <- DF_SAM %>% filter(porcionCosecha == "A")

DF_SAM_SI <- DF_SAM_SI %>%
  filter(HarvestStep < numPlants/(2*numWorkers)) # aver esto debe ser menor a 125 (la mitad de su jornada)

DF_SAM_SF <- DF_SAM_SF %>%
  filter(HarvestStep >= numPlants/(2*numWorkers)) # aver esto debe ser menor a 125 (la mitad de su jornada)

DF_SAM <- rbind(DF_SAM_A, DF_SAM_SF, DF_SAM_SI)

DF_SAM$porcionCosecha[DF_SAM$porcionCosecha =="A"] <- "Asynchronous"
DF_SAM$porcionCosecha[DF_SAM$porcionCosecha =="S_I"] <- "Synchronous" 
DF_SAM$porcionCosecha[DF_SAM$porcionCosecha =="S_F"] <- "Synchronous Final" 

##o remove the SF, to have the simpler versin
DF_SAM <- DF_SAM %>%
  filter(porcionCosecha != "Synchronous Final")

#the cacluatin was made with the square values, so we have to tkae the rootsquare
DF_SAM$DistanceW <- sqrt(DF_SAM$DistanceW)  


```


Then we take specifically the data corresponding to the moment of harvest. 
```{r}

DF_TOTAL = DF_SAM %>%
  filter(Time ==5.5)

rep <- length(unique(DF_TOTAL$Rep))

DF_TOTAL$Conteo <- 1

#we remove the 0 values as they dont make sense
DF_TOTAL <- DF_TOTAL %>%
  filter(!is.na(DistanceW))%>%
  filter(DistanceW != 0)

#for better visualiztin we round only integer values
DF_TOTAL$DistanceW <- round(DF_TOTAL$DistanceW,0)  


####we create a new column to report the new infections 

DF_TOTAL$Infection <- 0
DF_TOTAL$Infection[DF_TOTAL$Rust =="1"] <- "No Infection" 
DF_TOTAL$Infection[DF_TOTAL$Rust =="0"] <- "No Infection"
DF_TOTAL$Infection[DF_TOTAL$Rust =="0.5"] <- "New Infection"


#these lines of code can be used to run a proxy

#DF_TOTAL_PROXY <- DF_TOTAL %>%
#  filter(porcionCosecha == "Asynchronous")%>%
#  filter(numPlants == 2000)%>%
#  filter(Infection == "New Infection")%>%
#  filter(Rep %in% c(0,1,2,3,4,5))%>%
#  filter(DistanceW <1.1)
#DF_TOTAL <- DF_TOTAL_PROXY
```


We do the general visualization of paths:

```{r}
FIG_PATH_GEN<- DF_TOTAL %>% 
    filter(Rep == 0)%>%
    filter(numPlants == 500 |numPlants == 2000 | numPlants == 5000)%>% #solo un ejepmplo
    filter(WorkerID != 0)%>% 
    arrange(WorkerID, HarvestStep)%>%  #importante para que se orden por pasos, y despues se hace por worker!!
    rowwise() %>% 
    ggplot(aes(x= X, y = Y, group=WorkerID)) +
    geom_path(aes(col= WorkerID),size=1)+
    geom_point(size=1)+ # es importante que sea path, porque así lo hace según coo estan ordenados los
    scale_color_viridis_d()+
    facet_grid(porcionCosecha ~numPlants) +
    theme(panel.spacing = unit(0.8, "lines"), text = element_text(size = 15))+
    theme_bw()+
    theme(strip.background = element_rect(fill = "white"))+ 
    theme(text = element_text(size = 25))+
    theme(legend.position = "none") +
    labs(x= "X", y= "Y", col= "Worker")
  
  ggsave(FIG_PATH_GEN,filename=paste("../../output/graficas/SUP_FIG/", "path_GENERAL.png", sep=""),  height = 12, width = 18) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).
```

```{r}
FIG_PATH_2000_todos<- DF_TOTAL %>% 
  #filter(HarvestStep <160)%>% #ultimo 160 plantas de ahi
  filter(Rep == 2)%>%
 # filter(numWorkers =="1 worker")%>%
  filter(numPlants == 2000)%>% #solo un ejepmplo
  filter(WorkerID != 0)%>% 
  arrange(WorkerID, HarvestStep)%>%  #importante para que se orden por pasos, y despues se hace por worker!!
  rowwise() %>% 
  ggplot(aes(x= X, y = Y, group=WorkerID)) +
  #geom_path(aes(col= as.character(Infection)),size=1.5, alpha= 0.8)+
  geom_path(aes(col= as.character(WorkerID)),size=1.5, alpha= 0.8)+
  geom_point(size=1.5)+ # es importante que sea path, porque así lo hace según coo estan ordenados los
      scale_color_viridis_d()+

  theme(panel.spacing = unit(0.8, "lines"))+
  theme_bw()+
  facet_wrap(~porcionCosecha, nrow = 3) +
  theme(text = element_text(size = 25))+
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )+ 
  labs(x= "X (m)", y= "Y (m)", col= "Rust")

ggsave(FIG_PATH_2000_todos,filename=paste("../../output/graficas/PATH/", "path_plants_2000_w1_todos.png", sep=""),  height = 10, width = 6) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).


```


```{r}
FIG_PATH_2000_W1<- DF_TOTAL %>% 
  #filter(HarvestStep <160)%>% #ultimo 160 plantas de ahi
  filter(Rep == 2)%>%
  # filter(numWorkers =="1 worker")%>%
  filter(numPlants ==3000)%>% #solo un ejepmplo
  filter(WorkerID == "W_4")%>% 
  arrange(WorkerID, HarvestStep)%>%  #importante para que se orden por pasos, y despues se hace por worker!!
  rowwise() %>% 
  ggplot(aes(x= X, y = Y, group=WorkerID)) +
  geom_path(col= "black",size=1.5, alpha= 0.7)+
  geom_point(size=1.5)+ # es importante que sea path, porque así lo hace según coo estan ordenados los
  #scale_color_viridis_c()+
  scale_color_manual(values = colorsDis2)+
  theme(panel.spacing = unit(0.8, "lines"))+
  theme_bw()+
  facet_wrap(~porcionCosecha, nrow = 3) +
  theme(text = element_text(size = 25))+
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )+ 
  labs(x= "X (m)", y= "Y (m)", col= "Rust")

ggsave(FIG_PATH_2000_W1,filename=paste("../../output/graficas/PATH/", "path_plants_3000_1Worker.png", sep=""),  height = 10, width = 6) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).

```

Now, we will do the aggregate to generate the histogram manually


```{r}
#total_AG agregates the distance values per:
#numplant, numWorkers, infection, distnaceW, porcionCosecha, SimID, rep
#and then from that have a frec abs (so we remove the x, y coodrinates)

DF_TOTAL_AG_PRE <- DF_TOTAL %>%
  group_by(numPlants, numWorkers,  Infection, DistanceW, porcionCosecha, SimID, Rep) %>%
  summarise(FrecAbs =sum(Conteo))

#hen we add the frec, as the value in telation o the number of jharvester plantws (2*../numplans)

DF_TOTAL_AG_PRE$Frec <- 2* DF_TOTAL_AG_PRE$FrecAbs/(DF_TOTAL_AG_PRE$numPlants)

#el 2 es porque realmente es la mitad del numbero de plantas

#and then, we group these values per repetition

#now we complete the combinatns opf distanfes

DF_TOTAL_AG_PRE <- DF_TOTAL_AG_PRE %>%
  ungroup() %>%
  complete(DistanceW, nesting(numPlants, numWorkers,  Infection, porcionCosecha, Rep, SimID))

############################

DF_TOTAL_AG_PRE$Frec[is.na(DF_TOTAL_AG_PRE$Frec)] <- 0

DF_TOTAL_AG <- DF_TOTAL_AG_PRE %>%
  group_by(numPlants, numWorkers,  Infection, DistanceW, porcionCosecha, SimID) %>%
  summarise(MeanFrec =mean(Frec, na.rm = TRUE), SDFrec =sd(Frec, na.rm = TRUE))

##despues de completar y de hacer el agregamiento bueno deben quedar una cantidad de rengones
## con sentido. Completar hace que le agegues 0 en donde no había nada. 
## eneste caso, tenemos numPlans/numWorkers (5)+ Infection (2)* DistanceW (116)* porcionCosecha (2) =   2320 renglnones

#finally, we add a column to add the cumulative values 
DF_TOTAL_AG <- DF_TOTAL_AG %>%
  group_by(Infection, numPlants, porcionCosecha) %>%
  mutate(FrecCUM = cumsum(MeanFrec))

```



```{r}

#this super aggregate does not consider the infection division. We just sum both valus!

DF_SUPER_AG <- DF_TOTAL_AG%>%
  group_by(numPlants, numWorkers, DistanceW, porcionCosecha, SimID) %>%
  summarise(MeanFrecTotal = sum(MeanFrec), MeanFrecCUM = sum(FrecCUM))

write.csv(DF_SUPER_AG, paste("../../output/graficas/PATH/", "DF_SUPER_AG", ".csv"))
```

```{r}
#here I am goinf to run a test to see the influence of the number or repretitions on the final values of mean and sd


DF_TOTAL_AG_PRE$FrecAbs[is.na(DF_TOTAL_AG_PRE$FrecAbs)] <- 0



DF_STATS_REP <- data.frame()

for (i in 0:max(DF_TOTAL_AG_PRE$Rep)){
  DF_i <-DF_TOTAL_AG_PRE %>%
    filter(Rep<i+1)  #so the repetitions go from 0 to 29, and the index goes 
  
  DF_STATS_REP_i <- DF_i %>%
    ungroup()%>%
    group_by(numPlants, porcionCosecha) %>%
    summarise(wMean = weighted_mean(x= DistanceW, w=FrecAbs), 
           wSD = weighted_sd(x= DistanceW, w=FrecAbs), 
           NumRep = i+1)
  
  DF_STATS_REP <- rbind(DF_STATS_REP,  DF_STATS_REP_i)
  
}


DF_STATS_REP_L <- DF_STATS_REP %>%
  gather(key = "Stat", value = "value", wMean, wSD)




FIG_STAT_REP <- DF_STATS_REP_L %>% 
  ggplot(aes(x= NumRep, y = value)) +
  geom_line(aes(group = porcionCosecha))+
  geom_point(aes(col= porcionCosecha)) + 
    scale_color_manual(values =mycols2)+
  theme_bw()+
  facet_grid(Stat~numPlants, scales = "free_y") +
  theme(text = element_text(size = 25))+
  theme(strip.background = element_rect(fill = "white"))+ 
  scale_alpha(guide = 'none')+
      labs(color= "Harvesting Scenario", x= "Number of repetitions", y= "Step-length distribution") +
  ggtitle("Density (Plants/ha)") +
  theme(plot.title = element_text(hjust = 0.5, size = 20))



ggsave(FIG_STAT_REP,filename=paste("../../output/graficas/SUP_FIG/", "meanSD_rep.png", sep=""),  height = 7, width = 20) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).

```




```{r}
FIG_HIST_G_B_GEN <- DF_SUPER_AG %>%
    filter(MeanFrecTotal !=0)%>%

  filter((numPlants== 500) | (numPlants== 2000) |(numPlants== 5000))%>%
  ggplot(aes(x= DistanceW)) +
  geom_col(aes(y = MeanFrecTotal),
             color= "black", fill= "gray", position = "stack")+
#  xlim(0, 110)+
  ylim(0, 0.7)+
  facet_wrap(~porcionCosecha*numPlants, ncol = 3)+
  scale_fill_manual(values =colorsDis)+
  scale_color_manual(values =colorsDis)+
  theme_bw() +
  theme(text = element_text(size = 25))+
  theme(legend.position = "none")+
  theme(strip.background = element_rect(fill = "white"))+ 
  scale_alpha(guide = 'none')+
      labs(fill= "", x= bquote("Step length (m)"), y= "Proportion of Steps")

 ggsave(FIG_HIST_G_B_GEN,filename=paste("../../output/graficas/PATH/", "HISTO_GENERAL", ".png", sep=""),  height =7, width = 12) 

```


```{r eval=FALSE, include=FALSE}


DF_SIZE_STEP <- read.csv("../../data/DF_CUM_EDITADO.csv", header = TRUE)

FIG_SS <- DF_SIZE_STEP %>%
  ggplot(aes(x= DistanceW)) +
  geom_point(aes(y = MeanFrecCUM), color = "black")+
  geom_line(aes(y = MeanFrecCUM,  color= as.factor(porcionCosecha)))+
  theme_bw() +
  facet_wrap(~numPlants, ncol = 5)+
  theme(text = element_text(size = 25))+
  theme(legend.position = "none")+
  theme(strip.background = element_rect(fill = "white"))+ 
  scale_alpha(guide = 'none')+
      labs(fill= "", x= bquote("Step length (m)"), y= "Proportion of Steps")




```




```{r}

datos_TOTALES <- data.frame("Median" = 0, 
               "Mean" = 0,
                 "SD" = 0,
               "Mode" = 0,
               "pC" = 0, 
               "nP" =0 )

getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

for (nP in unique(DF_SUPER_AG$numPlants)){
  for (pC in unique(DF_SUPER_AG$porcionCosecha)){
    
    DF_SUPER_TEMP <- DF_SUPER_AG %>%
      filter((numPlants== nP) & (porcionCosecha == pC)) %>%
      filter(MeanFrecTotal !=0)
    
    DF_TOTAL_TEMP <-DF_TOTAL%>%
      filter((numPlants== nP) & (porcionCosecha == pC))
    
    CAJADIST_B<- DF_TOTAL_TEMP%>%
  ggplot(aes(x= DistanceW, y= as.character(porcionCosecha)))+
  geom_violin(fill= "#EEEEEE")+ 
  geom_point(aes(), shape= 21, fill= "gray", color= "black", size= 2, alpha = 0.8)+
  theme_bw()+
    scale_fill_manual(values =colorsDis)+
  theme(text = element_text(size = 25))+ 
  theme(axis.ticks.y = element_blank(),
        axis.text.y = element_blank())+
  theme(legend.position = "none")+
  xlim(0, 110)+
  labs(x= "Step length (m)", y= "", fill= "")


FIG_HIST_G_B <- DF_SUPER_TEMP %>%
  ggplot(aes(x= DistanceW)) +
  geom_col(aes(y = MeanFrecTotal),
             color= "black", fill= "gray", position = "stack")+
  xlim(0, 110)+
  ylim(0, 0.45)+
  scale_fill_manual(values =colorsDis)+
  scale_color_manual(values =colorsDis)+
  theme_bw() +
  theme(text = element_text(size = 25))+
  theme(legend.position = "none")+
  theme(strip.background = element_rect(fill = "white"))+ 
  scale_alpha(guide = 'none')+
      labs(fill= "", x= bquote("Step length (m)"), y= "Proportion of Steps")


HIS_COM_B<- FIG_HIST_G_B + annotation_custom(ggplotGrob(CAJADIST_B), xmin = 15, xmax = 100, ymin = 0.1, ymax = 0.4)
    
    
  #  ggsave(FIG_HIST_G,filename=paste("../../output/graficas/PATH/", "DisHIST_", "nP_", nP, "pC_", pC, ".png", sep=""),  height = 8, width = 14) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).
    ggsave(HIS_COM_B,filename=paste("../../output/graficas/PATH/", "DisFINAL_", "nP_", nP, "pC_", pC, ".png", sep=""),  height = 5, width = 7) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).
    
    
   
    
   datos <- data.frame("Median" = median(DF_TOTAL_TEMP$DistanceW), 
               "Mean" = mean(DF_TOTAL_TEMP$DistanceW),
                 "SD" = sd(DF_TOTAL_TEMP$DistanceW),
               "Mode" = getmode(DF_TOTAL_TEMP$DistanceW),
               "pC" = pC, 
               "nP" = nP)
    
   datos_TOTALES <- rbind(datos_TOTALES, datos)
   print(datos_TOTALES)
    
  }
}

write.csv(datos_TOTALES, paste("../../output/graficas/PATH/", "measures_TOTALES", ".csv"))


```



This is the section about cumulative trajectory


```{r}
DF_ARRANGED <- DF_TOTAL %>%
  select(HarvestStep, DistanceW, Rep, numPlants, HarvestModel, porcionCosecha, WorkerID, Infection, numWorkers)%>%
  dplyr::mutate(pasoLargo =   round(as.integer(DistanceW/25)/(DistanceW/25))) #truco para que todo valga 1 si es mayor a 18 reportado así como salto laog

DF_CUM <- DF_ARRANGED %>%
  group_by(Rep, numPlants, HarvestModel, porcionCosecha)%>%
  arrange(numPlants, HarvestModel, porcionCosecha, Rep, HarvestStep, WorkerID, numWorkers) %>% 
  dplyr::mutate(cs = cumsum(DistanceW))%>% 
  dplyr::mutate(cumPasoLargo = cumsum(pasoLargo))


#DF_CUM$PerStep <- 100*DF_CUM$HarvestStep/250

#
DF_CUM_A <- DF_CUM %>%
  filter(porcionCosecha == "Asynchronous") %>%
  mutate(PerStep = 100*HarvestStep/250)%>%
  mutate(PerArbBerry = 100*(numPlants/2 - (HarvestStep*numWorkers))/(numPlants))

DF_CUM_SI <- DF_CUM%>%
  filter(porcionCosecha == "Synchronous")%>%
  mutate(PerStep = 100*HarvestStep/250)%>%
  mutate(PerArbBerry = 100*(numPlants - (HarvestStep*numWorkers))/(numPlants))

DF_CUM_SF <- DF_CUM%>%
  filter(porcionCosecha == "Synchronous Final")%>%
  mutate(PerStep = 100*HarvestStep/250-100)%>%
  mutate(PerArbBerry = 100*(numPlants - (HarvestStep*numWorkers))/(numPlants))


DF_CUM <- rbind(DF_CUM_A, DF_CUM_SI, DF_CUM_SF)


rm(DF_CUM_A)
rm(DF_CUM_SI)
rm(DF_CUM_SF)

#DF_CUM$ArbNoCos <- DF_CUM$numPlants - DF_CUM$HarvestStep

#DF_CUM$PerCos <- 100 -(DF_CUM$ArbNoCos/DF_CUM$numPlants *100)
```


```{r}
FIG_CUM <- DF_CUM %>%
  #filter(Rep ==2)%>%
  #filter(WorkerID == "W_2")%>%
  #filter(numPlants== 2000)%>%
  ggplot(aes(x= PerArbBerry, y = DistanceW)) +
  geom_line(aes(color= as.factor(Rep), group= WorkerID))+
  facet_grid(porcionCosecha ~numPlants) +
  theme_bw() +
  scale_color_viridis_d()+
    scale_x_reverse()+
  #geom_segment(aes(x=1.5, y=0, xend= 1.5, yend= 0.025, size = 0.2, color= "Black")+
  theme(text = element_text(size = 25))+
  theme(strip.background = element_rect(fill = "white"))+ 
  theme(legend.position = "None")+
  labs(x= "% Harvested trees", y= "Size of step per worker")


ggsave(FIG_CUM,filename=paste("../../output/graficas/SUP_FIG/", "FIG_PROGRESSION.png", sep=""),  height = 8, width = 20)



FIG_CUM_2000 <- DF_CUM %>%
  filter(Rep ==2)%>%
 # filter(WorkerID == )%>%
  filter(numPlants== 2000)%>%
  ggplot(aes(x= PerArbBerry, y = DistanceW)) +
  geom_line(aes(group = WorkerID, color = WorkerID))+
  facet_wrap(~porcionCosecha, nrow = 3, scales = "free_x") +
  #facet_wrap(~porcionCosecha, nrow = 3) +

  theme_bw() +
  scale_color_viridis_d()+
  #geom_segment(aes(x=1.5, y=0, xend= 1.5, yend= 0.025, size = 0.2, color= "Black")+
  theme(text = element_text(size = 25))+
  scale_x_reverse()+
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )+
  theme(legend.position = "none")+
  labs(x= "% Trees with berries", y= "Step length per worker (m)", color= "Rust")


ggsave(FIG_CUM_2000,filename=paste("../../output/graficas/PATH/", "FIG_PROGRESSION_2000.png", sep=""),  height = 10, width = 6)


```



Here is for the supplementary mateiral
```{r}
FIG_INF <- DF_TOTAL_AG %>%
  filter(Infection == "New Infection")%>%
    filter((numPlants== 500) | (numPlants== 2000) |(numPlants== 5000) )%>%

  ggplot(aes(x= DistanceW)) +
   # geom_line(aes(y= FrecCUM, group =SimID), color= "black", size=2)+
  #geom_line(aes(y= FrecCUM, color=porcionCosecha, group =SimID), size=1)+
  geom_ribbon(aes(ymin=FrecCUM- SDFrec, ymax=FrecCUM+SDFrec, group= SimID, 
                  fill= porcionCosecha, linetype= porcionCosecha), color= "black")+
  xlim(0, 20)+
  #ylim(0, 0.45)+
  facet_wrap(~numPlants, nrow = 1)+
  scale_color_manual(values =mycols2)+
    scale_fill_manual(values =mycols2)+
  scale_linetype_manual(values= c(1,5, 0))+

  theme_bw() +
  theme(text = element_text(size = 20))+
#  theme(legend.position = "none")+
  theme(strip.background = element_rect(fill = "white"))+ 
  scale_alpha(guide = 'none')+
 # theme(legend.position="bottom")+
      labs(fill= "Harvesting Scenario", x= 'Step length', y= "Proportion of Infective steps", color= "Harvesting scenario", linetype = "Harvesting Scenario")


 ggsave(FIG_INF,filename=paste("../../output/graficas/DIF_RUST/", "INF_HAR.png", sep=""),  height = 5, width = 16)

```


This chunks is only for a visualizaton of the whole plot. Do not activate
```{r}

wholePlot <- 0

n= 0
if (wholePlot ==1){
  
  #DF_SAM = DF_sample
  
  for(nP in unique(DF_SAM$numPlants)){
    for(tiempo in c(0,timeMAX)){
      FIG_PLOT <- DF_SAM %>%
        filter(numPlants == nP)%>%
        filter(Rep ==0)%>%
        filter(Time == tiempo) %>%
        add_row(porcionCosecha = "Asynchronous",  Rep= 0,   ID= 999999,  X= NA,  Y=NA , Rust= 0.5)%>% ##ESte es un truquito para que siempre hayan 3 colores en cada graficas, porque le 0.5 siempre desaprece
        add_row(porcionCosecha = "Synchronous",  Rep= 0,   ID= 9999999,  X= NA,  Y=NA , Rust= 0.5)%>%
        ggplot()+
        geom_point(aes(x=X , y= Y, color= as.character(Rust)), size= 2)+
        ggtitle("")+
        facet_wrap(~porcionCosecha, ncol=2)+
        theme(text = element_text(size = 25))+
        theme_bw()
      
      
      ggsave(FIG_PLOT,filename=paste("../../output/figurasLattice/",nP, "plotFigure_", tiempo, ".png",sep=""), height = 8, width = 16) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).
      n= n+1
    }
  }
}

```



Now, this section is for the infection process Part II (is independent of Part I)






```{r}
DF_AV <- read.csv("../../data/DF_spatialAverage_complete.csv", header = TRUE)

#we change control model to "no har"

DF_AV$HarvestTime[DF_AV$HarvestModel =="control"] <- "control"
DF_AV$porcionCosecha[DF_AV$HarvestModel =="control"] <- "control"
#DF_AV$numWorkers[DF_AV$HarvestModel =="control"] <- "NoH" 


DF_AV$porcionCosecha[DF_AV$porcionCosecha =="A"] <- " Asynchronous"
DF_AV$porcionCosecha[DF_AV$porcionCosecha =="S_F"] <- " Synchronous Final" 
DF_AV$porcionCosecha[DF_AV$porcionCosecha =="S_I"] <- " Synchronous" 

DF_AV <- DF_AV %>%
  filter(DF_AV$porcionCosecha != " Synchronous Final")

DF_AV$HarvestModel[DF_AV$HarvestModel =="closeness"] <- "harvest"



DF_AV$Rust <- DF_AV$Rust*100 #lo pasamos a un porcentage de infeccion para tener una intepretacion as sencilla 


#Our first verification is the number of lines for DF_AV
# we need to have a data frame with 
# [(3 porcCosecha (A, SI, SF)* 1 harvestingTime * 1 numWorkers) + (1 control)]* 5 numPlants * 25 (time max*2+1) times * 30 rep
#[3 * 1 * 1 +1) * 5* 25* 30 rep
# 4 * 5 * 25 * 30
# 15000  rows
```

Here I added a independent chunk to show how the results are roust in 30 repetitions


```{r}


DF_INF_REP <- data.frame()

for (i in 0:max(DF_AV$Rep)){
  DF_i <-DF_AV %>%
    filter(Rep<i+1)%>%
    filter(Time == 12)

  DF_INF_REP_i <- DF_i %>%
    ungroup()%>%
    group_by(numPlants, numWorkers, HarvestModel, HarvestTime,porcionCosecha, SimID) %>%
    summarise(AverageRust = mean(Rust), SD_Rust = sd(Rust), NumRep = i+1)
  DF_INF_REP <- rbind(DF_INF_REP,  DF_INF_REP_i)
  
}


DF_INF_REP_L <- DF_INF_REP %>%
  gather(key = "Stat", value = "value", AverageRust, SD_Rust)




FIG_INF_REP <- DF_INF_REP_L %>% 
  ggplot(aes(x= NumRep, y = value)) +
  geom_line(aes(group = porcionCosecha))+
  geom_point(aes(col= porcionCosecha)) + 
  scale_color_manual(values = mycols3)+
  #scale_color_manual(values = colorsDis2)+
 # theme(panel.spacing = unit(0.8, "lines"))+
  theme_bw()+
  facet_grid(Stat~numPlants, scales = "free_y") +
  theme(text = element_text(size = 25))+
  theme(strip.background = element_rect(fill = "white"))+ 
  scale_alpha(guide = 'none')+
      labs(color= "Harvesting Scenario", x= "Number of repetitions", y= "Rust infection")+
   ggtitle("Density (Plants/ha)") +
  theme(plot.title = element_text(hjust = 0.5, size = 20))


ggsave(FIG_INF_REP,filename=paste("../../output/graficas/SUP_FIG/", "meanINF_rep.png", sep=""),  height = 7, width = 20) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).

```





```{r}
#here we summarize or average between all repetition- So
#DF_AV_MOD_AVR should be 15000/30 = 500 (combinations)

DF_AV_AVR <- DF_AV %>%
  group_by(numPlants, numWorkers, HarvestModel, HarvestTime,porcionCosecha, Time, SimID) %>%
  summarise(AverageRust = mean(Rust), SD_Rust = sd(Rust))

```

```{r}
############FIRST FIGURES, time seires, final time, control paarte
#these figures are only plotted without the number of workers that did not show a relevant difference
# so we are plotting only the last time == 12

timeMAX <- 12


FIG_RUST <- DF_AV%>%
  filter(Time == timeMAX)%>%
  filter(numWorkers !=5)%>%
  filter(HarvestTime ==5 |HarvestTime =="control")%>% 
  mutate(porcionCosecha = (ifelse(porcionCosecha == "control", "Control", porcionCosecha)))%>% 
  ggplot(aes(x= as.factor(HarvestModel), y= Rust))+
  geom_boxplot(color= "black", aes(fill= as.character(porcionCosecha)))+ 
  ggtitle("")+
  facet_wrap(~ numPlants, nrow=1, labeller = label_both)+
  scale_fill_manual(values = mycols3_white)+
  theme_bw() +
  theme(text = element_text(size = 25))+
  theme(strip.background = element_rect(fill = "white"))+ 
  ylim(0,100)+
  labs(x= "Density (Plants/ha)", y= "Average Rust", fill= "Coffee Maturation")

ggsave(FIG_RUST,filename=paste("../../output/graficas/SUP_FIG/", "rust_plants_abs", ".png", sep=""),  height = 10, width = 16) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).

#
```



```{r}
FIG_SLI_time <- DF_AV_AVR %>% 
  filter(numWorkers !=5)%>% 
  filter(HarvestTime ==5|HarvestTime =="control")%>% 
  filter(numPlants == 500 | numPlants == 2000 |numPlants == 5000)%>% 
  
  mutate(porcionCosecha = (ifelse(porcionCosecha == "control", "Control (no harvesting)", porcionCosecha)))%>% 
  ggplot(aes(x= Time, color= as.character(porcionCosecha) ,
             fill= as.character(porcionCosecha)
             ))+
  geom_ribbon(color= "black", aes( 
                  ymin=AverageRust-SD_Rust, ymax=AverageRust+SD_Rust, linetype= as.character(porcionCosecha)),alpha=0.9) +
  #  geom_line(size= 1, aes(y= AverageRust))+
  ggtitle("")+
  facet_wrap(~ numPlants, nrow =1)+
  theme(panel.spacing = unit(1, "cm"))+
  scale_linetype_manual(values= c(1, 5,2, 0))+
  scale_fill_manual(values = mycols3_white)+
  scale_color_manual(values = mycols3)+
  theme_bw()+
  theme(text = element_text(size = 20))+
  theme(strip.background = element_rect(fill = "white"))+
  theme(panel.spacing = unit(1, "cm"))+
  labs(x= "Time step (t)", y= "Average Rust (%)", color= "Harvesting scenario", fill= "Harvesting scenario", linetype="Harvesting scenario" )
ggsave(FIG_SLI_time,filename=paste("../../output/graficas/DIF_RUST/", "rust_time_abs", ".png", sep=""),  height = 5, width = 16) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc)
```


```{r}
DF_MODvsCON_GEN <- DF_AV %>%
  filter(Time == HarvestTime |Time == timeMAX) %>%
  group_by(Rep, numPlants)%>% #son las vairables que quedan y sobre esos escenarios, vamos a hacer las diferencias entre modelos
  summarise(Rust = Rust, ModCo_Rust = ((Rust - Rust[HarvestModel=="control"])), Per_Rust = ((Rust - Rust[HarvestModel=="control"])/Rust[HarvestModel=="control"]),
            porcionCosecha = porcionCosecha, HarvestTime = HarvestTime, numWorkers = numWorkers, Time= Time)  # esto es solo para que despues de leer por condicion, regrese...?

#esta deberia tener:

# [(2 porcCosecha (A and S)* 5 harvestingTime * 2 numWorkers) + 1 control que se filtra]* 5 numPlants * * 30 rep
#[21] * 5 * 30  = 3150 PARA EL HARVEST MAX#
#[(2 porcCosecha (A and S)* 5 harvestingTime * 2 numWorkers) 5 numPlants * * 30 rep
  #3000 para el harvest time. Esto porque aqui no se pone el control. 
  #6150

```

```{r}
DF_MODvsCON_GEN <- DF_MODvsCON_GEN%>%
filter(porcionCosecha != "control")

```

```{r}
FIG_DIF_CONTROL <- DF_MODvsCON_GEN %>%
  filter(Time == timeMAX)%>%
 # filter(numWorkers == 1)%>%
  filter(numPlants!=4000)%>%
  mutate(porcionCosecha = (ifelse(porcionCosecha == "control", " No harvesting (control)", porcionCosecha)))%>% 
 # mutate(porcionCosecha = (ifelse(porcionCosecha == "0.5", "With large steps", porcionCosecha)))%>% 
#  mutate(porcionCosecha = (ifelse(porcionCosecha == "1", "Without large steps", porcionCosecha)))%>% 
  ggplot(aes(x= as.factor(HarvestTime), y= ModCo_Rust))+
  geom_boxplot(color = "black", aes(fill= porcionCosecha, linetype= porcionCosecha), position = "dodge")+ 
  ggtitle("")+
  facet_wrap(~numPlants, nrow = 1, strip.position = "bottom")+
  scale_fill_manual(values = mycols2)+ 
  scale_linetype_manual(values= c(1,5, 0))+
  ylim(0, 18)+
  theme_bw() +
  theme(text = element_text(size = 20),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())+
  #theme(strip.background = element_rect(fill = "white"))+ 
  theme(strip.background = element_blank())+
  theme(panel.spacing = unit(0, "cm"))+
  #theme(legend.position = "none")+
  labs(x= "Density (Plants/ha)", y= "Rust Increase (Scenario-Control)", fill= "Harvesting Scenario", linetype="Harvesting Scenario" )

ggsave(FIG_DIF_CONTROL,filename="../../output/graficas/DIF_RUST/ModelvsControl.png",  height = 5, width = 12) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).

```



Para el suplmentario!! 


```{r eval=FALSE, include=FALSE}

densidades = length(unique(DF_AV$numPlants))


DF_DIF <- DF_AV %>%
  filter(HarvestModel != "control")%>%  #we remove the contorl, we do not need it.
  filter(Time == timeMAX)

#this chunks is removed  but i kept the logic just in case
#DF_AvsSF <- DF_DIF %>%
#  filter(porcionCosecha != " Synchronous")
#DF_AvsSF$Rust[DF_AvsSF$porcionCosecha == " Synchronous Final"] <- DF_AvsSF$Rust[DF_AvsSF$porcionCosecha == " Synchronous Final"]*-1
#DF_AvsSF <- DF_AvsSF %>%
#  group_by(Rep, numPlants) %>%
#  summarise(PerIncrease = sum(Rust))
#DF_AvsSF$DIF <- "A-SF"


DF_DIF$Rust[DF_DIF$porcionCosecha == "Synchronous"] <- DF_DIF$Rust[DF_DIF$porcionCosecha == "Synchronous"]*-1

DF_DIF <- DF_DIF %>%
  group_by(Rep, numPlants) %>%
  summarise(PerIncrease = sum(Rust))


```

```{r eval=FALSE, include=FALSE}
FIG_DIF_MODELS <- DF_DIF%>%
  ggplot(aes(x= as.factor(numPlants), y= PerIncrease))+
  geom_boxplot(color= "black", aes())+
  ggtitle("")+
  #facet_wrap(~numPlants, nrow=2)+
  scale_fill_manual(values =  c("white", "#CCCCCC", "#666666"))+
  geom_segment(aes(x=0, y=0, xend= 6, yend=0), size = 0.2, color= "DarkRed")+
  theme_bw() +
  #theme(legend.position = "none")+
  theme(text = element_text(size = 25))+
  theme(strip.background = element_rect(fill = "white"))+
  labs(x= "Density (Plants/ha)", y= "Average Rust Difference")

ggsave(FIG_DIF_MODELS,filename="../../output/graficas/DIF_RUST/dif_models.png",  height = 8, width = 10) # ID will be the unique identifier. and change the extension from .png to whatever you like (eps, pdf etc).

```



####para volvero codigo plano (y poderlo correr desde la terminal)

```{r}
library(knitr)
purl("../../src/grapherCodes/figuresLattice.Rmd", output= "../../src/grapherCodes/figuresLattice.R")

```

```{r}
## ESTO LO DEJO PARA CUANDO QUEIRA USAR LA FUCNION LAF
#DF_TOTAL_AG$DIF_CUM <- NULL

#DF_TOTAL_AG <- DF_TOTAL_AG %>%
 # group_by(numPlants, numWorkers, Infection, porcionCosecha, SimID)%>%
  #mutate(DIF_CUM = FrecCUM - lag(FrecCUM))

```
